\documentclass[letterpaper,11pt]{article}
\usepackage{helvet, calc, amssymb, tabularx, hyperref}
\pagestyle{empty}
%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{0in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.35in}
\setlength{\evensidemargin}{-0.25in}

%Item spacing

\usepackage{enumitem}
\setlist{nolistsep}
\newcommand{\indentitem}{\setlength\itemindent{25pt}}

%tabularx column type
\newcolumntype{Y}{>{\centering}X}

%-----------------------------------------------------------

\title{Resume}

\begin{document}
	\begin{center}
		\textbf{\huge TREVOR OPHELDERS}
		\noindent\makebox[\linewidth]{\rule[3pt]{\textwidth - 50pt}{1pt}} 
		\begin{tabularx}{0.76\textwidth}{Y c Y c c}
			3A Software Engineering & $\blacklozenge$ & t.ophelders@gmail.com & $\blacklozenge$ & (647) 267-9944
		\end{tabularx}		
	\end{center}
	
	\section*{\small PROFILE}
	\begin{itemize}
        \item Experience working in Python, Java, C, C++, BASH, JavaScript, HTML and CSS gained through both work and schooling
		\item Intricate knowledge of computer hardware and software design
		\item Strong communication skills derived from daily interactions with supervisors and team members
		\item Able to consistently make tight deadlines without the need of constant supervision
	\end{itemize}
	
	\section*{\small EXPERIENCE}
  		\hspace*{25pt}\textbf{Software Developer}, Economical Insurance, Kitchener, ON, Sept. - Dec. 2014
        \begin{itemize}
        	\indentitem
            \item Contributed to the development of multiple Java EE applications, harnessing the JDBC API \hspace*{25pt}to communicate with SQL databases 
            \item Developed utility scripts in both Python and BASH that were used to automate repeated tasks
            \item Collaborated on designing web applications in JavaScript, HTML and CSS
        \end{itemize}
        
        \vspace{7pt}
		\hspace*{7pt}\textbf{Software Developer}, Northern Digital Incorporated, Waterloo, ON, Jan. - Apr. 2014
		\begin{itemize}
			\indentitem
			\item Designed and developed Java/C++ application software in the medical technology field
			\item Worked on applications designed to graphically display and manipulate highly accurate 3D \hspace*{25pt}position data
			\item Participated in the design of applications that used the Java Native Interface, along with select \hspace*{25pt}libraries to allow for direct communication between NDI hardware and software
		\end{itemize}
			
		\vspace{7pt}
		\hspace*{7pt}\textbf{Quality Assurance Analyst}, NexJ Systems, Toronto, ON, Apr. - Aug. 2013
		\begin{itemize}
			\indentitem
			\item Ensured the quality of numerous CRM software projects
			\item Used SQL to test mock databases; learned how to effectively model client data
			\item Participated in various aspects of Agile Methodologies, including Scrum Teams and Standups
		\end{itemize}
		
	\section*{\small ACTIVITIES AND INTERESTS}
		\hspace*{25pt}\textbf{GitHub Profile:} \url{https://github.com/TOphelders}
        
		\vspace*{7pt}
		\hspace*{7pt}\textbf{Brother Andre Science and Engineering Club Member} (Sept. 2011 – June 2012)
		\begin{itemize}
			\indentitem
			\item Competed in the First Robotics Competition with a team built and programmed robot
			\item Took partial responsibility for the coding, focusing on autonomously aiming and shooting a ball \hspace*{25pt}into a basket
		\end{itemize}
		\vspace*{7pt}
		\hspace*{25pt}Enjoy reading, coding, Super Smash Bros. Melee, snowboarding, playing guitar, hiking
        
	\section*{\small EDUCATION}
		\hspace*{25pt}\textbf{Candidate for Bachelor of Software Engineering}, Co-operative Program, University of \\\hspace*{25pt}Waterloo, Waterloo, ON, Sept. 2012 - present
		
	\section*{\small AWARDS AND ACHIEVEMENTS}
		\begin{itemize}
			\item President's Scholarship, University of Waterloo, Waterloo, ON, Sept. 2012
		\end{itemize}
\end{document}